Speed and strength of epidemic intervention

### 2019-09-11 doc/speedstrength.tex
Meeting with Daniel
Notes during meeting

\documentclass{article}\usepackage[]{graphicx}\usepackage[]{color}
\usepackage[top=1in,left=1in, right = 1in, footskip=1in]{geometry}

@@

\newcommand{\comment}[3]{\textcolor{#1}{\textbf{[#2: }\textit{#3}\textbf{]}}}
\newcommand{\jd}[1]{\comment{cyan}{BMB}{#1}}
\newcommand{\swp}[1]{\comment{magenta}{SWP}{#1}}

@@

>>>>

\documentclass[12pt]{article}\usepackage[]{graphicx}\usepackage[]{color}
\usepackage[top=1in,left=1in, right = 1in, footskip=1in]{geometry}

@@

\newcommand{\comment}[3]{\textcolor{#1}{\textbf{[#2: }\textit{#3}\textbf{]}}}
\newcommand{\jd}[1]{\comment{cyan}{JD}{#1}}
\newcommand{\swp}[1]{\comment{magenta}{SWP}{#1}}

@@

\section{To do}

JD to edit once-through by 2019 Sep 18. I don't know if we can meet.

Add a bigger perspective from Eaton and Hallett (SWP can start on that if time). Look also (less important) and Bellan and Dushoff's follow-up to Hollingsworth.

Talk about speed-like and strength-like estimates of an epidemic (e.g., HIV growth rate vs.~measles mean susceptibility) and of an intervention.

JD to do a condom calculation framing.
